---
title: "Walking & cycling exposure in Walthamstow: 2013 v. 2021"
author: "James Smith"
output:
  html_document:
    toc_float: true
    toc: true
    toc_depth: 4
    collapsed: false
date: "`r format(Sys.time(), '%Y-%m%-%d %H%:%M')`"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs", output_file ="exposure.html") })
---

this document descibes the process of calcualting walking and cycling exposure for a number of typical routes within the London Borough of Waltham Forest.

### Preparation

Load libraries
```{r setup}
rm(list = ls())

## Load libraries
library('knitr')
library("googleway")
library("gepaf")
library("sp")
library('raster')
library('ggplot2')
library('geosphere')
library('sf')
library('reshape2')
library('leaflet')
library('mapview')
library('kableExtra')

## rmarkdown::render('make_exposure.Rmd', output_dir = "docs", output_file ="exposure.html")
```

### Data import

Import routes

```{r import_routes}

exposure_routes <- read.csv('exposure_journeys.csv',
                            stringsAsFactors = F)

exposure_routes[exposure_routes$via_array == '','via_array'] <- NA
```

### Route calculation, offest, and exposure calculation

Make a loop to calculate the routes and extract the concentrations. If seggregated==true, then the route is offset by the variable 'offset'

```{r start_loop, message=F, warning=F}

start_time        <- Sys.time() + 1000
via_array         <- NA


for (i in 1:nrow(exposure_routes)) {

# Journey parameters
start_lat         <- exposure_routes[i,]$start_lat
start_lon         <- exposure_routes[i,]$start_lon

if (!is.na(exposure_routes[i,]$via_array)) {via_array <- as.list(strsplit(as.character(exposure_routes[i,]$via_array), ";")[[1]]) } else {via_array <- NA}

end_lat           <- exposure_routes[i,]$end_lat
end_lon           <- exposure_routes[i,]$end_lon
mode              <- as.character(exposure_routes[i,]$mode)
seggregated       <- exposure_routes[i,]$seggregated

## take account of where in the road the journey is taking place
if (mode == 'walk'    & seggregated == 'no')  {offset <- 6}
if (mode == 'walk'    & seggregated == 'yes') {offset <- 8}
if (mode == 'bicycle' & seggregated == 'no')  {offset <- 4}
if (mode == 'bicycle' & seggregated == 'yes') {offset <- 6}


# EPSG strings we might need
latlong                 <- "+init=epsg:4326"
ukgrid                  <- "+init=epsg:27700"
google_projected        <- "+init=epsg:3857 +proj=merc +a=6378137 +b=6378137 +lat_ts=0.0 +lon_0=0.0 +x_0=0.0 +y_0=0 +k=1.0 +units=m +nadgrids=@null +no_defs"

# Take the start/end data and get a route from Google
if ('walk' %in% mode)     { source("routing/walking.R") }
if ('bicycle' %in% mode)  { source("routing/cycling.R") }

rm(start_lat, start_lon, end_lat, end_lon)

if ('walk' %in% mode) {
  result <- walk_result
  rm(walk_result)
  duration <- walk_duration
  rm(walk_duration)
} else {
  result <- cycle_result
  rm(cycle_result)
  duration <- cycle_duration
  rm(cycle_duration)
}

##### In here is where we calculate the offset for where the journey is taking place compared to the centre of the road
##### https://stackoverflow.com/questions/50275195/draw-a-parallel-line-in-r-offset-from-a-line
#### Only want to do this if seggregated == yes

coordinates(result) <- ~lon + lat
proj4string(result) =  CRS(latlong)
result <- spTransform(result, ukgrid)

segment.shift <- function(x, y, d){
#  
  # calculate vector
  v <- c(x[2] - x[1],y[2] - y[1])
#  
  # normalize vector
  v <- v/sqrt((v[1]**2 + v[2]**2))
#  
  # perpendicular unit vector
  vnp <- c( -v[2], v[1] )
  
  return(list(x =  c( x[1] + d*vnp[1], x[2] + d*vnp[1]), 
              y =  c( y[1] + d*vnp[2], y[2] + d*vnp[2])))
  
}

x <- result@coords[,1]
y <- result@coords[,2]

xn <- numeric( (length(x) - 1) * 2 )
yn <- numeric( (length(y) - 1) * 2 )

for ( p in 1:(length(x) - 1) ) {
  xs <- c(x[p], x[p+1])
  ys <- c(y[p], y[p+1])
  new.s <- segment.shift( xs, ys, offset)
  xn[(p-1)*2+1] <- new.s$x[1] ; xn[(p-1)*2+2] <- new.s$x[2]
  yn[(p-1)*2+1] <- new.s$y[1] ; yn[(p-1)*2+2] <- new.s$y[2]
}

new_result   <- data.frame(x = xn,
                           y = yn)
coordinates(new_result) <- ~x+y
proj4string(new_result) = CRS(ukgrid)
new_result              <- spTransform(new_result, latlong)
new_result              <- data.frame(new_result)
new_result$id           <- unique(result$id)
new_result$line         <- unique(result$line)
new_result$mode         <- unique(result$mode)

result <- new_result
rm(new_result, new.s, offset, x, xn, xs, y, yn, ys, segment.shift)
names(result)[1:2] <- c('lon', 'lat')

##### End of the help from stackoverflow

coordinates(result) <- ~lon + lat
proj4string(result) = CRS(latlong)
result <- spTransform(result, ukgrid) 

## This makes a spatialline from the points for the result
x <- lapply(split(result, result$id), function(x) Lines(list(Line(coordinates(x))), result$id[1L]))
lines <- SpatialLines(x)
data <- data.frame(id = unique(result$id))
rownames(data) <- data$id
result <- SpatialLinesDataFrame(lines, data)
proj4string(result) = CRS(ukgrid)
rm(x, lines, data) 


## How many minutes long was the bicycle and walk journeys

timeslots                <- data.frame(id = unique(result$id), time = seq.POSIXt(start_time, start_time + duration, "min"))

## Now want to split the line into a point per minute

result                    <- st_as_sf(result)
result$id                 <- exposure_routes[i,]$journey_id

if (i == 1) {line_result <- result} else {line_result <- rbind(line_result, result)}

result                   <- st_line_sample(result, n = nrow(timeslots), type = 'regular')
result                   <- suppressWarnings(st_set_crs(result, 27700))
result                   <- data.frame(as(result, 'Spatial'))

## Now some harmonisation stuff to get the car, walk and bus all the same format so can join them together
result$id                 <- exposure_routes[i,]$journey_id
result$mode               <- mode
result$line               <- NA
result                    <- cbind(result, timeslots)
names(result)             <- c('easting', 'northing', 'id', 'mode', 'line', 'id_2', 'time')
result                    <- result[,c('id', 'mode', 'line', 'time', 'easting', 'northing')]
result$year               <- exposure_routes[i,]$year
coordinates(result)       <- ~easting + northing
proj4string(result)       <- CRS(ukgrid)

# Now get our pollutant files

## 2013 concentration maps
if (exposure_routes[i,]$year == 2013) {
wf_2013_no2              <- raster('air_quality/no2_2013.asc')
crs(wf_2013_no2)         <- CRS(ukgrid)
wf_2013_nox              <- raster('air_quality/nox_2013.asc')
crs(wf_2013_nox)         <- CRS(ukgrid)
wf_2013_pm10             <- raster('air_quality/pm10_2013.asc')
crs(wf_2013_pm10)        <- CRS(ukgrid)
wf_2013_pm25             <- raster('air_quality/pm25_2013.asc')
crs(wf_2013_pm25)        <- CRS(ukgrid)

# Extract concentrations
no2                                   <- result
no2@data$pollutant                    <- 'no2'
no2@data$concentration                <- extract(wf_2013_no2, no2@coords, method = 'bilinear')

pm25                                  <- result
pm25@data$pollutant                   <- 'pm25'
pm25@data$concentration               <- extract(wf_2013_pm25, pm25@coords, method = 'bilinear')

pm10                                  <- result
pm10@data$pollutant                   <- 'pm10'
pm10@data$concentration               <- extract(wf_2013_pm10, pm10@coords, method = 'bilinear')

nox                                   <- result
nox@data$pollutant                    <- 'nox'
nox@data$concentration                <- extract(wf_2013_nox, nox@coords, method = 'bilinear')

result                                <- rbind.SpatialPointsDataFrame(no2, pm25, nox, pm10)

rm(wf_2013_no2, wf_2013_nox, wf_2013_pm10, wf_2013_pm25,nox, no2, pm25, pm10)

}

## 2020 concentration maps 
if (exposure_routes[i,]$year == 2020) {
wf_2020_no2              <- raster('air_quality/no2_2020.asc')
crs(wf_2020_no2)         <- CRS(ukgrid)
wf_2020_nox              <- raster('air_quality/nox_2020.asc')
crs(wf_2020_nox)         <- CRS(ukgrid)
wf_2020_pm10             <- raster('air_quality/pm10_2020.asc')
crs(wf_2020_pm10)        <- CRS(ukgrid)
wf_2020_pm25             <- raster('air_quality/pm25_2020.asc')
crs(wf_2020_pm25)        <- CRS(ukgrid)

# Extract concentrations
no2                                   <- result
no2@data$pollutant                    <- 'no2'
no2@data$concentration                <- extract(wf_2020_no2, no2@coords, method = 'bilinear')

pm25                                  <- result
pm25@data$pollutant                   <- 'pm25'
pm25@data$concentration               <- extract(wf_2020_pm25, pm25@coords, method = 'bilinear')

pm10                                  <- result
pm10@data$pollutant                   <- 'pm10'
pm10@data$concentration               <- extract(wf_2020_pm10, pm10@coords, method = 'bilinear')

nox                                   <- result
nox@data$pollutant                    <- 'nox'
nox@data$concentration                <- extract(wf_2020_nox, nox@coords, method = 'bilinear')

result                                <- rbind.SpatialPointsDataFrame(no2, pm25, nox, pm10)

rm(wf_2020_no2, wf_2020_nox, wf_2020_pm10, wf_2020_pm25,nox, no2, pm25, pm10)

}

if (i == 1) {final_result <- result} else {final_result <- rbind.SpatialPointsDataFrame(final_result, result)}

rm(timeslots, duration, result, via_array)

}
```

Bind the results we've made together with the original parameter data, and delete some variables that aren't needed anymore

```{r bind_results}

final_result$time <- NULL
final_result$line <- NULL
final_result      <- merge(final_result, exposure_routes[,c('journey_id', 'name', 'seggregated')], by.x = 'id', by.y = 'journey_id')
rm(i, google_projected, latlong, mode, seggregated, ukgrid)


```

### Results

The summary of the routes and years are shown.

```{r aggregate_results}

summary_results <- aggregate(concentration ~ name + mode + year + pollutant + seggregated, data=final_result, FUN=mean)

names(summary_results) <- c('Route', 'Mode', 'Year', 'Pollutant', 'Seggregated', 'Mean Exposure (ug/m3)')

summary_results[order(summary_results$Route, summary_results$Pollutant, summary_results$Year),] %>% kable(row.names = F) %>% kable_styling()
```

```{r make_points_to_sf}
final_result    <- st_as_sf(final_result)
```

```{r add_lines_to_summary}

summary_results <- merge(summary_results, exposure_routes[,c('journey_id', 'name')], by.x = 'Route', by.y = 'name')

summary_results <- merge(summary_results, line_result, by.x = 'journey_id', by.y ='id')

summary_results <- st_sf(summary_results[,-c(8)],st_sfc(summary_results$geometry))

```

Now make some plots of the results

```{r make_plots}
plot <- list()

for (i in 1:length(unique(final_result$name))) {
  
  route_name <- unique(final_result$name)[i]
  
  plot[[i]] <- ggplot(final_result[final_result$name == route_name,], 
                      aes(x = as.factor(year), y = concentration, fill = seggregated)) +
    geom_boxplot() +
    facet_wrap(name~pollutant, ncol = 4, scales = 'free_y') +
    xlab('Year') +
    theme(plot.subtitle = element_text(vjust = 1), 
    plot.caption = element_text(vjust = 1), 
    panel.grid.major = element_line(colour = "gray92"), 
    panel.grid.minor = element_line(colour = "gray92"), 
    axis.title = element_text(size = 14), 
    axis.text = element_text(size = 14, colour = "black"), 
    axis.text.y = element_text(size = 14), 
    plot.title = element_text(size = 14), 
    legend.title = element_text(size = 13), 
    panel.background = element_rect(fill = NA, 
        colour = "black", linetype = "solid"), 
    plot.background = element_rect(colour = NA),
    strip.text.x = element_text(size = 8),
    strip.background = element_blank())

}
```

Example 1 - Chingford to Leyton (Concentration plots)

```{r chingford_to_leyon_concs}
plot[[1]]
```

Example 1 - Chingford to Leyton (Spatial plots)

```{r chingford_to_leyton_spatial}

final_result <- st_set_crs(final_result, 27700)
final_result <- st_transform(final_result, 4326)

example_2013 <- final_result[final_result$pollutant == 'no2' & final_result$name == 'Chingford to Leyton' & final_result$year == 2013,]

example_2020 <- final_result[final_result$pollutant == 'no2' & final_result$name == 'Chingford to Leyton' & final_result$year == 2020 & final_result$seggregated == 'yes',]

qpal <- colorQuantile("YlOrRd", c(example_2013$concentration, example_2020$concentration), n = 7)

qpal <- colorNumeric(
  palette = c("green","yellow","orange","red"),
  domain = c(example_2013$concentration, example_2020$concentration))

leaflet()%>%
  addProviderTiles(providers$Esri.WorldTopoMap)%>%
  addFeatures(example_2013,
              group = '2013',
              fillColor = qpal(example_2013$concentration),
              color="transparent",
              fillOpacity = 0.7,
             popup = paste0(as.character(round(example_2013$concentration,0)),' µg/m<sup>3</sup>')) %>%
  addFeatures(example_2020,
              group = '2020',
              fillColor = qpal(example_2020$concentration),
              color="transparent",
              fillOpacity = 0.7,
              popup = paste0(as.character(round(example_2020$concentration,0)), ' µg/m<sup>3</sup>')) %>%
  addLayersControl(baseGroups = c('2013', '2020')) %>%
  addLegend(pal=qpal,values=c(example_2013$concentration, example_2020$concentration),title="NO2 (µg/m<sup>3</sup>)") %>%
  addControl('<strong>Exposure to NO<sub>2</sub> while cycling between Chingford <br> & Leyton has dropped by 24% between 2013<br>and 2020 due to improvements in air<br> quality, and the introduction of seggregated <br> cycle lanes.</strong>', position = "topleft")

rm(example_2013, example_2020)

```
All routes

```{r map_of_routes}

line_result <- st_set_crs(line_result, 27700)
line_result <- st_transform(line_result, 4326)

leaflet()%>%
  #addProviderTiles(providers$Esri.WorldTopoMap)%>%
  #addProviderTiles(providers$Esri.NatGeoWorldMap) %>%
  addTiles() %>%
  addFeatures(line_result[line_result$id %in% exposure_routes[exposure_routes$mode == 'bicycle',]$journey_id,],
              group = 'Bike Routes',
              color = 'red',
              popup = as.character(exposure_routes[exposure_routes$journey_id %in% line_result[line_result$id %in% exposure_routes[exposure_routes$mode == 'bicycle',]$journey_id,]$id,]$name),
              opacity = 0.3) %>%
    addFeatures(line_result[line_result$id %in% exposure_routes[exposure_routes$mode == 'walk',]$journey_id,],
                group = 'Walk Routes',
                color = 'blue',
                popup = as.character(exposure_routes[exposure_routes$journey_id %in% line_result[line_result$id %in% exposure_routes[exposure_routes$mode == 'walk',]$journey_id,]$id,]$name),
                 opacity = 0.3) %>%
  addLayersControl(baseGroups = c('Bike Routes', 'Walk Routes'))
   

```