---
title: "Waltham Forest Ward Concentrations"
author: "James Smith"
output:
  html_document:
    toc: true
    toc_depth: 4
date: "`r format(Sys.time(), '%Y-%m%-%d %H%:%M')`"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs", output_file ="ward_concentrations.html") })
---

This document outlines the creation of calculating mean Ward-level concentrations for the [London Borough of Waltham Forest](https://walthamforest.gov.uk/). The air quality input files are based upon data from the [LAEI 2013](https://data.london.gov.uk/dataset/london-atmospheric-emissions-inventory-2013), updated with new speed data provided by the Borough, and forward-cast to 2020.

### Set-up
```{r setup, include=FALSE}
rm(list=ls())

### Loading any missing libraries

library(rvest)
library(stringr)
library(raster)
library(rgdal)
library(rgeos)
devtools::install_github("tidyverse/ggplot2")
library(ggplot2)
library(sf)
library(rmarkdown)
```

### Data importing

Get the ward boundaries

```{r Get ward boundaries}
ukgrid      <- "+init=epsg:27700"
latlong     <- "+init=epsg:4326"

authorities <- data.frame(authority_name = c('Waltham Forest'),
                          stringsAsFactors = F)

###  getting a geojson of UK wards from governmant data portal

url                 <- 'https://opendata.arcgis.com/datasets/d5c9c1d89a5a44e9a7f88f182ffe5ba2_2.geojson'
wards               <- readOGR(dsn = url, layer = "d5c9c1d89a5a44e9a7f88f182ffe5ba2_2")
wards               <- spTransform(wards, ukgrid)
wards               <- wards[wards$lad16nm %in% authorities$authority_name,]

```

Import the air quality files

```{r import airquality}

no2_2013_raster <- raster('T:/Projects/WalthamForest/Modelling/PostLAEI2013_WF/2013/ASCII/PostLAEI_2013_WFSpeedUpdate_NO2.asc')
pm25_2013_raster <- raster('T:/Projects/WalthamForest/Modelling/PostLAEI2013_WF/2013/ASCII/PostLAEI_2013_WFSpeedUpdate_PM25.asc')

no2_2020_raster <- raster('T:/Projects/WalthamForest/Modelling/PostLAEI2013_WF/2020/ASCII/no2_2020.asc')
pm25_2020_raster <- raster('T:/Projects/WalthamForest/Modelling/PostLAEI2013_WF/2020/ASCII/pm25_2020.asc')

```

Check rasters

```{r check rasters}
plot(no2_2013_raster)
plot(wards, add=T)
title('2013 NO2')

plot(pm25_2013_raster)
plot(wards, add=T)
title('2013 PM25')

plot(no2_2020_raster)
plot(wards, add=T)
title('2020 NO2')

plot(pm25_2020_raster)
plot(wards, add=T)
title('2020 PM25')
```

### Data processing

Crop the rasters and check they look ok

```{r crop rasters}
wards_extent      <- extent(st_bbox(wards)$xmin-40, st_bbox(wards)$xmax+40, 
                      st_bbox(wards)$ymin-40, st_bbox(wards)$ymax+40)

no2_2013_raster   <- crop(no2_2013_raster, wards_extent)
pm25_2013_raster  <- crop(pm25_2013_raster, wards_extent)
no2_2020_raster   <- crop(no2_2020_raster, wards_extent)
pm25_2020_raster  <- crop(pm25_2020_raster, wards_extent)

plot(no2_2013_raster)
plot(wards, add=T)
title('2013 NO2')

plot(pm25_2013_raster)
plot(wards, add=T)
title('2013 PM25')

plot(no2_2020_raster)
plot(wards, add=T)
title('2020 NO2')

plot(pm25_2020_raster)
plot(wards, add=T)
title('2020 PM25')

```

Extract the concentrations per ward

```{r get means by ward, warning=F}

wards$mean_no2_2013    <- extract(no2_2013_raster, wards, fun=mean)
wards$mean_pm25_2013   <- extract(pm25_2013_raster, wards, fun=mean)

wards$mean_no2_2020    <- extract(no2_2020_raster, wards, fun=mean)
wards$mean_pm25_2020   <- extract(pm25_2020_raster, wards, fun=mean)
```

Prep work for plotting

```{r make some plots}
wards             <- st_as_sf(wards)

wards$wd16nm       <- as.character(wards$wd16nm)
wards$id          <- 1:nrow(wards)
ward_centroids    <- data.frame(id = as.character(wards$id),
                                  name = as.character(wards$wd16nm),
                                  st_coordinates(st_centroid(wards)))
names(ward_centroids)[3:4] <- c('x','y') 
```

### Mapping 

The wards

```{r map of wards}
ggplot(wards, aes(colour = wd16nm)) +
  geom_sf() +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.background = element_blank(),
        legend.background = element_rect(size=0.2, linetype="solid", colour ="black")) +
  scale_colour_manual(values = rep('black', 20), name = 'Ward name', labels = paste(1:20, wards$wd16nm)) +
  geom_text(data = ward_centroids, aes(x, y, label = id), colour='black')
```

Mean 2013 NO2 concentrations

```{r no2_2013_ward_map}
ggplot(wards) +
  geom_sf(aes(fill=mean_no2_2013)) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.background = element_blank(),
        legend.background = element_rect(size=0.2, linetype="solid", colour ="black"))
```

Mean 2020 PM2.5 concentrations

```{r pm25_2013_ward_map}
ggplot(wards) +
  geom_sf(aes(fill=mean_pm25_2013)) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.background = element_blank(),
        legend.background = element_rect(size=0.2, linetype="solid", colour ="black"))
```

Mean 2013 NO2 concentrations

```{r no2_2020_ward_map}
ggplot(wards) +
  geom_sf(aes(fill=mean_no2_2020)) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.background = element_blank(),
        legend.background = element_rect(size=0.2, linetype="solid", colour ="black"))
```

Mean 2020 PM2.5 concentrations

```{r pm25_2020_ward_map}
ggplot(wards) +
  geom_sf(aes(fill=mean_pm25_2020)) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.background = element_blank(),
        legend.background = element_rect(size=0.2, linetype="solid", colour ="black"))
```

### data output

Write concentrations to a CSV

```{r output to a CSV}
st_geometry(wards) <- NULL
write.csv(data.frame(wards[,c('wd16cd', 'wd16nm', 'mean_no2_2013', 'mean_pm25_2013', 'mean_no2_2020', 'mean_pm25_2020')]), 'csv_outputs/wf_ward_concs.csv', row.names = F)
```

[Download final CSV from here](https://raw.githubusercontent.com/JimShady/waltham_forest/master/csv_outputs/wf_ward_concs.csv)